---
title: "ForSysXR automatic report"
output: html_document
date: "`r Sys.Date()`"
author: "ForSys Consortium"
---

<!-- --- -->
<!-- params: -->
<!--   commands_given_print: commands_given_print -->
<!-- always_allow_html: true -->
<!-- --- -->


```{css, echo=FALSE}
    body .page-inner {
      max-width: 65% !important;
      margin-left: auto;
      margin-right: auto
      
    }
    body .body-inner {
      max-width: 100% !important;
      margin-left: auto;
      margin-right: auto
      
    }
    body {
      max-width: 100% !important;
      margin-left: auto;
      margin-right: auto
    }
```  

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warnings=FALSE)


#load workspace
#load("C:/Users/almeidbr/Desktop/forsysxr_tutorial/del_files/my_work_space.RData")

## Get user data
#data <- params$data
#report_config <- params$report_config
#response <- params$response
#commands_given_print <- params$commands_given_print

```

```{r global_options, include=FALSE}
## Load library
library(data.table)
library(rmarkdown)
library(knitr)


## Get user data
#commands_given_print <- params$commands_given_print
#commands_given_print_final_use <- commands_given_print_final
#load workspace




```

```{r, echo=FALSE}


load("my_work_space_vs2.RData")
```



```{r, echo=FALSE}


htmltools::img(src = knitr::image_uri(paste(system.file("help/figures", package = "ForSysXR"),"FORSYS_logo_small.png",sep="/")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width: 143px; height: 128px') # Added width and height as CSS
```

## Settings used

The following report refers to the run named **`r (last_name)`**, that used the R package ForSysXR. 

The table below refers to the settings used in the ForSysX run. Note that these values are not captured by the inputs given by the user in the R script, but rather captures the values reported in the Summary text file that is exported by ForSysX. Nevertheless, these values must match the ones inputed by the user. Review them carefully.
  
```{r }

  collapse_rows_df <- function(df, variable){
  group_var <- enquo(variable)
  df %>%
    group_by(!! group_var) %>%
    mutate(groupRow = 1:n()) %>%
    ungroup() %>%
    mutate(!!quo_name(group_var) := ifelse(groupRow == 1, as.character(!! group_var), "")) %>%
    select(-c(groupRow))
  }
  
  
  
  
introduction_table%>%
    collapse_rows_df(Parameter)%>%
    knitr::kable(caption="Values used to run ForSysX as reported in the Summary text file generated by ForSysX")
  
  
  
```

## Map of projects created

The figure below shows the location of the projects created, color-codded by their ranking or priority. The project number 1 has a higher contribution for the objective(s) than project number 2, etc. Note that projects may include stands that are not targeted for treatment.




```{r echo=FALSE}
htmltools::tagList(projects_plot_leaflet)
```




## Attainment figures

The figures below show the attainment per project (top) and the cumulative attainment (bottom) for the effects stored. This figure
is of particular interest when the effect is showed as PCP.
  
```{r, echo=FALSE, fig.cap=paste("Figure 1.", attainment_fig_constraint1, sep=" "),fig.height = 10,  fig.align = "center"}
suppressWarnings(print(plot_attainment_per_project_ggarranged))

```


The figure below show the attainment for all effects reported, per project. This figure is of particular interest when the effect is showed as PCP.

```{r, echo=FALSE, fig.cap=paste("Figure 4.", sep=" "),fig.height = 5,  fig.align = "center"}
suppressWarnings(print(plot_attainment_per_project_barplot))

```




## Additional resources

### Amount of constraint treated

```{r, echo=FALSE, fig.cap=paste("Figure 2.", caption_fig_constraint1, sep=" "),fig.height = 10,  fig.align = "center"}
suppressWarnings(print(plot_treated_constraint_in_proj_ggarrange))

```

```{r, echo=FALSE}
if(exists("my_plot_variables_bars_report")){
  asis_output("### Costum variables\\n")}
```


```{r, echo=FALSE, fig.cap=paste("Figure 3.", caption_report_variables, sep=" "),fig.height = fig.height_variables_bars,  fig.align = "center"}
if(exists("my_plot_variables_bars_report")){
suppressWarnings(print(my_plot_variables_bars_report))}

```






### R Code used in set_forsysx_run

The inputed R code in the function set_forsysx_run is displayed below
```{r}
#cat(paste(commands_given_print), sep="\n",fill = TRUE,include=FALSE)
# 
# my_list_input_variable<-get_input_names_long()
# 
# 
# all_matching_set_forsysx_run <- grep("set_forsysx_run", my_list_input_variable$Last.command)
# #select the highest - most recent command
# 
# most_recent_set_forsysx_run <- max(all_matching_set_forsysx_run)
# 
# commands_given_print <- my_list_input_variable$Last.command[most_recent_set_forsysx_run:length(my_list_input_variable$Last.command)]

cat(commands_given_print,fill = TRUE)#,include=FALSE)
```


## Disclaimer and additional support

This report is automatically generated by ForSysXR and has not been validated. The figures and analysis shown here must be
carefully analyzed and validated before drawing to conclusions. The USDA Forest Services are not responsible for the use and
interpretation of any of the ForSys family products.

If you found any error or issue, please open a new issue [here](https://github.com/forsys-sp/ForSysXR/issues) and provide a replicable example of your data and run settings.

For further support please contact Michelle Day (michelle.day@usda.gov) or Alan Ager (alan.ager@oregonstate.edu)    

```{r, include = FALSE, echo=FALSE,message = FALSE,warning = FALSE}
(rm(list = ls()[grep("attainment_fig_constraint1", ls())], envir = globalenv()))
    (rm(list = ls()[grep("caption_fig_constraint1", ls())], envir = globalenv()))
    (rm(list = ls()[grep("caption_fig1", ls())], envir = globalenv()))
```
