---
title: "ForSysXR explore report"
output: html_document
date: "`r Sys.Date()`"
author: "ForSys Consortium"
---

<!-- --- -->
<!-- params: -->
<!--   commands_given_print: commands_given_print -->
<!-- always_allow_html: true -->
<!-- --- -->



  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warnings=FALSE)


#load workspace
#load("C:/Users/almeidbr/Desktop/forsysxr_tutorial/del_files/my_work_space.RData")

## Get user data
#data <- params$data
#report_config <- params$report_config
#response <- params$response
#commands_given_print <- params$commands_given_print

```

```{r global_options, include=FALSE}
## Load library
library(data.table)
library(rmarkdown)
library(knitr)


## Get user data
#commands_given_print <- params$commands_given_print
#commands_given_print_final_use <- commands_given_print_final
#load workspace




```

```{r, echo=FALSE}


load("my_work_space_vs2.RData")
```



```{r, echo=FALSE}


htmltools::img(src = knitr::image_uri(paste(system.file("help/figures", package = "ForSysXR"),"forsys_consortium_logo.png",sep="/")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width: 394px; height: 125px') # Added width and height as CSS
```

## Settings used

The following report was generated automatically by the explore function of ForSysXR package.

The figure below represents the stands that will be considered for the ForSys run assuming the parameters set by the user. The map is interactive and the user can choose the layer they want to visualize. Multiple layers can be plotted at the same time to allow intrepretation about the considered area after more than one constraint set. Note that the maps are not cumulative. This means the layer only represents the considered stands given a specific parameter, rather than a set of parameters, even when overlaying layers.
  


```{r echo=FALSE, fig.cap=paste("Figure 1.", sep=" ")}
#suppressWarnings(print(available_plot_leaflet))
tagList(available_plot_leaflet)
```



## Table of considered stands

  
```{r }

  collapse_rows_df <- function(df, variable){
  group_var <- enquo(variable)
  df %>%
    group_by(!! group_var) %>%
    mutate(groupRow = 1:n()) %>%
    ungroup() %>%
    mutate(!!quo_name(group_var) := ifelse(groupRow == 1, as.character(!! group_var), "")) %>%
    select(-c(groupRow))
  }
  
  
  
  
area_considered_table%>%
    #collapse_rows_df(Parameter)%>%
    knitr::kable(caption="Table 1. Area and objective values considered in ForSys run when each constraint is accounted individually and all together (last row). The row Stands total (first row) represents the total area or objective in the stand shapefile, ignoring all constaints given. Value between parenthesis represent the percentage of the total")
  
  
  
```


## Map of considered stands in ForSys

The figure below shows the stands considered for treatment in the ForSys run defined by the user. It reflects the availability, exclusion, and threshold fields defined. The figure relates with the area reported in the last row (Combination of criteria) in Table 1.

```{r echo=FALSE, fig.cap=paste("Figure 2.", sep=" ")}
#suppressWarnings(print(available_plot_leaflet))
tagList(combination_area_sf_plot_leaflet)
```




```{r echo=FALSE, fig.cap=paste("Figure 2.", sep=" ")}
if(exists("landuse_landscape_ggarrange_plot")){
suppressWarnings(print(landuse_landscape_ggarrange_plot))  
}

```


```{r echo=FALSE, fig.cap=paste("Figure 2.", sep=" ")}
if(exists("landuse_considered_ggarrange_plot")){
suppressWarnings(print(landuse_considered_ggarrange_plot))  
}

```


```{r echo=FALSE, fig.cap=paste("Figure 2.", sep=" ")}
if(exists("landownership_landscape_ggarrange_plot")){
suppressWarnings(print(landownership_landscape_ggarrange_plot))  
}

```



```{r echo=FALSE, fig.cap=paste("Figure 2.", sep=" ")}
if(exists("landownership_considered_ggarrange_plot")){
suppressWarnings(print(landownership_considered_ggarrange_plot))  
}

```




## Disclaimer and additional support

This report is automatically generated by ForSysXR and has not been validated. The figures and analysis shown here must be
carefully analyzed and validated before drawing to conclusions. The USDA Forest Services are not responsible for the use and
interpretation of any of the ForSys family products.

If you found any error or issue, please open a new issue [here](https://github.com/forsys-sp/ForSysXR/issues) and provide a replicable example of your data and run settings.

For further support please contact Michelle Day: michelle.day@usda.gov

