---
title: "ForSysXR explore report"
output: html_document
date: "`r Sys.Date()`"
author: "ForSys Consortium"
---

<!-- --- -->
<!-- params: -->
<!--   commands_given_print: commands_given_print -->
<!-- always_allow_html: true -->
<!-- --- -->



  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warnings=FALSE)


#load workspace
#load("C:/Users/almeidbr/Desktop/forsysxr_tutorial/del_files/my_work_space.RData")

## Get user data
#data <- params$data
#report_config <- params$report_config
#response <- params$response
#commands_given_print <- params$commands_given_print

```

```{r global_options, include=FALSE}
## Load library
library(data.table)
library(rmarkdown)
library(knitr)


## Get user data
#commands_given_print <- params$commands_given_print
#commands_given_print_final_use <- commands_given_print_final
#load workspace




```

```{r, echo=FALSE}


load("my_work_space_vs2.RData")
```



```{r, echo=FALSE}


htmltools::img(src = knitr::image_uri(paste(system.file("help/figures", package = "ForSysXR"),"forsys_consortium_logo.png",sep="/")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width: 394px; height: 125px') # Added width and height as CSS
```

## Settings used

The following report was generated automatically by the explore function of ForSysXR package.

The table below refers to the settings used in the ForSysX run. Note that these values are not captured by the inputs given by the user in the R script, but rather capture the values reported in the Summary text file that is exported by ForSysX. Nevertheless, these values must match the ones inputed by the user. Review them carefully.
  


```{r echo=FALSE}
suppressWarnings(print(exclude_plot))
```



## Map of projects created

The figure below shows the location of the projects created, color-coded by their ranking or priority. The project number 1 has a higher contribution for the objective(s) than project number 2, etc.





## Disclaimer and additional support

This report is automatically generated by ForSysXR and has not been validated. The figures and analysis shown here must be
carefully analyzed and validated before drawing to conclusions. The USDA Forest Services are not responsible for the use and
interpretation of any of the ForSys family of products.

If you found any error or issue, please open a new issue [here](https://github.com/forsys-sp/ForSysXR/issues) and provide a replicable example of your data and run settings.

For further support please contact Michelle Day: michelle.day@usda.gov

